Results

### 2018-02-27 3-simus.Rmd
simus finished

```{r}
paste(sprintf("%.1e", 10^(-c(0, -log10(5e-8), exp(seq(log(0.1), log(100), length.out = 100))))), collapse = ", ")
PRS <- function(G, infos.chr, infos.pos, 
                pheno.all, covar.all, 
                ind.train, ind.test) {

>>>>

```{r}
10^(-c(0, -log10(5e-8), exp(seq(log(0.1), log(100), length.out = 100)))) %>%
  sprintf("%.1e", .) %>%
  paste(collapse = ", ")
```

```{r}
PRS <- function(G, infos.chr, infos.pos, 
                pheno.all, covar.all, 
                ind.train, ind.test) {

### 2018-02-27 4-results-simus.Rmd
simus finished

```{r}
boot <- function(x, n = 1e4, f = mean) {
  sd(replicate(n, f(sample(x, replace = TRUE))))
}
```

@@

  p2 <- cowplot::plot_grid(
    plot_extra("nb.preds", "Number of predictors"),
    plot_extra("timing", "Execution time (in seconds)"),
    ncol = 1, align = "hv", scale = 0.95, 
    labels = LETTERS[2:3], label_size = 15
  )

  p12 <- cowplot::plot_grid(
    p1 + theme(legend.position = "none"), p2, 
    ncol = 2, scale = 0.95, rel_widths = c(6, 4), 
    labels = c("A", ""), label_size = 15
  )

@@

ggsave("figures/supp-ttrees.pdf", scale = 1/90, width = 1400, height = 1060)
```

@@

ggsave("figures/supp-triple.pdf", scale = 1/90, width = 1400, height = 1060)
```

@@

ggsave("figures/supp-AUC-triple.pdf", scale = 1/90, width = 1242, height = 951)
```

@@

ggsave("figures/supp-AUC-logit-fancy.pdf", scale = 1/90, width = 1242, height = 951)
```

@@

ggsave("figures/supp-AUC-PRS-fancy.pdf", scale = 1/90, width = 1242, height = 951)
```

@@

### Correlation between predictive measures [MOVE TOP]

@@

```{r, fig.asp=0.5, out.width="95%", fig.width=16}
results3 %>%
  filter(method %in% c("logit-simple", "PRS-max")) %>%
  mutate(Parameters  = interaction(par.h2, par.dist, method, sep = " | ")) %>%
  myggplot(aes(AUC, pAUC, color = Parameters)) + 
  geom_point(size = 0.6, alpha = 0.5) +
  geom_smooth(aes(linetype = Parameters), method = "loess", se = FALSE, size = 2) +
  theme(legend.key.width = unit(3.5, "line"), 
        legend.direction = "horizontal") + 
  labs(y = "Partial AUC (specificity: [0.9, 1])") +
  theme(legend.position = "top")

@@

ggsave("figures/supp-AUC-chr6.pdf", scale = 1/90, width = 1153, height = 908)
```

@@

ggsave("figures/main-AUC-ntrain.pdf", scale = 1/90, width = 1050, height = 800)
```

>>>>

```{r}
boot <- function(x, n = 1e5, f = mean) {
  sd(replicate(n, f(sample(x, replace = TRUE))))
}
```

@@

  p2 <- cowplot::plot_grid(
    plot_extra("nb.preds", "Number of predictors"),
    plot_extra("timing", "Execution time (in seconds)"),
    ncol = 1, align = "hv", scale = 0.95, 
    labels = LETTERS[2:3], label_size = 20
  )

  p12 <- cowplot::plot_grid(
    p1 + theme(legend.position = "none"), p2, 
    ncol = 2, scale = 0.95, rel_widths = c(6, 4), 
    labels = c("A", ""), label_size = 20
  )

@@

ggsave("figures/supp-ttrees.pdf", scale = 1/100, width = 1400, height = 1060)
```

@@

ggsave("figures/supp-triple.pdf", scale = 1/100, width = 1400, height = 1060)
```

@@

ggsave("figures/supp-AUC-triple.pdf", scale = 1/110, width = 1242, height = 951)
```

@@

ggsave("figures/supp-AUC-logit-fancy.pdf", scale = 1/110, width = 1242, height = 951)
```

@@

ggsave("figures/supp-AUC-PRS-fancy.pdf", scale = 1/110, width = 1242, height = 951)
```

@@

### Correlation between predictive measures

@@

```{r, fig.asp=0.7, out.width="95%", fig.width=16}
results3 %>%
  filter(method %in% c("logit-simple", "PRS-max")) %>%
  mutate(Parameters  = interaction(par.h2, par.dist, method, sep = " | ")) %>%
  myggplot(aes(AUC, pAUC, color = Parameters)) + 
  geom_point(size = 0.6, alpha = 0.5) +
  geom_smooth(aes(linetype = Parameters), method = "loess", se = FALSE, size = 2) +
  theme(legend.key.width = unit(3.5, "line"), 
        legend.direction = "horizontal") + 
  labs(y = "Partial AUC (specificity: [0.9, 1])") +
  theme(legend.position = "top", axis.title = element_text(size = rel(2.2))) +

@@

ggsave("figures/supp-AUC-chr6.pdf", scale = 1/110, width = 1153, height = 908)
```

@@

ggsave("figures/main-AUC-ntrain.pdf", scale = 1/100, width = 1050, height = 800)
```
